### 2022-02-16 paper/paper.tex
fix typo

We now consider the problem of predicting the emotions of Twitter text.
This is a very different domain than the image problems considered above,
and demonstrates that the tree loss works across many domains.
We use the dataset collected by \citet{izbicki2019geolocating} and \citet{stoikos2020multilingual}.
This dataset contains all geolocated tweets written in more than 100 language sent over the 4 year period between October 2017 and October 2021---approximately $5.5\times10^9$ tweets in total.
Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
and then the goal is to predict the emoji given only the remaining text.
Since most emojis represent emotions,
the task of emoji prediction serves as a proxy for emotion prediction.

>>>>

We now consider the problem of predicting the emotions of Twitter text.
This is a very different domain than the image problems considered above,
and demonstrates that the tree loss works across many domains.
We use the dataset collected by \citet{izbicki2019geolocating} and \citet{stoikos2020multilingual}.
This dataset contains all geolocated tweets written in more than 100 languages sent over the 4 year period between October 2017 and October 2021---approximately $5.5\times10^9$ tweets in total.
Tweets in the dataset are preprocessed to have all emojis, usernames, and urls removed from the text,
and then the goal is to predict the emoji given only the remaining text.
Since most emojis represent emotions,
the task of emoji prediction serves as a proxy for emotion prediction.
